Wavelet Spatio-Temporal Change Detection on multi-temporal SAR images

### 2021-12-15 tex/paper.wecs/corrections_Aluisio/mudancas_texto_DEC2021.tex
corrections of Aluisio

LINE 9 "along" ==> "over"

@@

LINE 1 "After" ==> "The"

LINE 2 ", one of its byproducts is" ==> "results in"

LINE 3 ", of so" ==> "of the so"

@@

LINE 1 "can be" ==> "may be"

LINE 2 "analysis" ==> "analyses"

LINES 2-3 "different types of wavelet transform and basis" ==> "different wavelet bases"

LINE 3 "as well the use of" ==> "as well as the"

LINE 4 "for detail" ==> "of detail"

@@

LINE 1 "The most right-hand term in " ==> "The last term on the right-hand side of "

LINE 3 "regarding" ==> "and"

LINE 5 "the time" ==> "time"

LINE 8 "the spatial" ==> "spatial"

LINES 9-10 "the Pearson correlation coefficient rises as an convenient alternative" ==> 
"the Pearson correlation coefficient is an interesting alternative".

LINE -0 ", as explained earlier" ==> "[26]"

FORMULAS (2) e (3) Faltam pontos finais.

@@

LINES 1-2  "Consequen ... R ... assigned" ==> "Let R=[R_{kl}], where R_{kl} is assigned"

@@

LINE 1 "Let us define" ==> "Define"

LINE -2 "that for " ==> "that, for

ACRESCENTAR AQUI A IDEIA DE REGRESSAO ... ******Está no final do arquivo

@@

LINE 2 "distinct studies" ==> "studies"

@@

LINE 2 "identify" ==> "identifying"

@@

LINES -1-(-2) "Posterior ... out" XXXXX

@@

LINE 1 "Lastly, the" ==> "The"

@@

 LINES 1-2 "All the changes made that occur among subsequent" ==> "All changes between subsequent"

 LINE 3 "the "ones")" ==> " "ones")"

 LINE 4 "along ...instants" XXXXXXX

@@

 LINE 1 "images,"  ==> "images"

@@

 LINE 3 "The curves allow concluding that" ==> "We conclude that"

@@

 LINE -1 "to the competitors" ==> "both competitors"

@@

 LINE 1 "This sections demonstrates the WECS" ==> "This sections compares the performance of WECS"

LINE 2 "methods" XXXXXXX

LINE 3 "In detail, this application considers" ==> "We consider here

@@

 LINES 3-4 "Figures 9(a)-9(b)" ==> "Figures 6(a)-6(b)"

@@

 LINE 2 "it was" ==> "it is"

@@

 LINE -2 "Figure 7" ==> "Figure 8"

@@

 LINES 1-3 "After submitting the image series to the methods WECS, ECS, and TAAD, are obtained ... domain" ==> "Through the application WECS, ECS and TAAD to the image series, we obtain matrices R, \tilde{R} and A. They represent the spatially-localized change measures given by WECS, ECS and TAAD, respectively".

@@

 LINE 4 "kappa coefficient with basis" ==> "kappa coefficient based"

@@

 LINES 1-2 "the WECS method" ==> "WECS"

@@

 LINE 5 "the WECS method" ==> "WECS"

@@

 LINE 4 "than ECS and TAAD" ==> "than either ECS or TAAD".

 LINES 4-5 "the TAAD method" ==> "TAAD"

@@

 LINE 1 "the WECS method" ==> "WECS"

@@

 LINE 3-6 "studying energy correlation screening method with for distinct smoothing techniques; deducing change detection rates theoretically for a statistical models" ==> "extending energy correlation screening for distinct smoothing techniques; deducing sharp theoretical change detection rates for appropriate statistical models"

>>>>

* LINE 9 "along" ==> "over"

@@

* LINE 1 "After" ==> "The"

* LINE 2 ", one of its byproducts is" ==> "results in"

* LINE 3 ", of so" ==> "of the so"

@@

* LINE 1 "can be" ==> "may be"

* LINE 2 "analysis" ==> "analyses"

* LINES 2-3 "different types of wavelet transform and basis" ==> "different wavelet bases"

* LINE 3 "as well the use of" ==> "as well as the"

* LINE 4 "for detail" ==> "of detail"

@@

* LINE 1 "The most right-hand term in " ==> "The last term on the right-hand side of "

* LINE 3 "regarding" ==> "and"

* LINE 5 "the time" ==> "time"

* LINE 8 "the spatial" ==> "spatial"

* LINES 9-10 "the Pearson correlation coefficient rises as an convenient alternative" ==> 
"the Pearson correlation coefficient is an interesting alternative".

* LINE -0 ", as explained earlier" ==> "[26]"

* FORMULAS (2) e (3) Faltam pontos finais.

@@

* LINES 1-2  "Consequen ... R ... assigned" ==> "Let R=[R_{kl}], where R_{kl} is assigned"

@@

* LINE 1 "Let us define" ==> "Define"

* LINE -2 "that for " ==> "that, for

* ACRESCENTAR AQUI A IDEIA DE REGRESSAO ... ******Está no final do arquivo

@@

* LINE 2 "distinct studies" ==> "studies"

@@

* LINE 2 "identify" ==> "identifying"

@@

* LINES -1-(-2) "Posterior ... out" XXXXX

@@

* LINE 1 "Lastly, the" ==> "The"

@@

* LINES 1-2 "All the changes made that occur among subsequent" ==> "All changes between subsequent"

* LINE 3 "the "ones")" ==> " "ones")"

* LINE 4 "along ...instants" XXXXXXX

@@

* LINE 1 "images,"  ==> "images"

@@

* LINE 3 "The curves allow concluding that" ==> "We conclude that"

@@

* LINE -1 "to the competitors" ==> "both competitors"

@@

* LINE 1 "This sections demonstrates the WECS" ==> "This sections compares the performance of WECS"

* LINE 2 "methods" XXXXXXX

* LINE 3 "In detail, this application considers" ==> "We consider here

@@

* LINES 3-4 "Figures 9(a)-9(b)" ==> "Figures 6(a)-6(b)"

@@

* LINE 2 "it was" ==> "it is"

@@

* LINE -2 "Figure 7" ==> "Figure 8"

@@

* LINES 1-3 "After submitting the image series to the methods WECS, ECS, and TAAD, are obtained ... domain" ==> "Through the application WECS, ECS and TAAD to the image series, we obtain matrices R, \tilde{R} and A. They represent the spatially-localized change measures given by WECS, ECS and TAAD, respectively".

@@

* LINE 4 "kappa coefficient with basis" ==> "kappa coefficient based"

@@

* LINES 1-2 "the WECS method" ==> "WECS"

@@

* LINE 5 "the WECS method" ==> "WECS"

@@

* LINE 4 "than ECS and TAAD" ==> "than either ECS or TAAD".

* LINES 4-5 "the TAAD method" ==> "TAAD"

@@

* LINE 1 "the WECS method" ==> "WECS"

@@

* LINE 3-6 "studying energy correlation screening method with for distinct smoothing techniques; deducing change detection rates theoretically for a statistical models" ==> "extending energy correlation screening for distinct smoothing techniques; deducing sharp theoretical change detection rates for appropriate statistical models"
